Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-12-08 concurrency/CPP 2024/paper.tex
finished Conference/Publisher-Specific Requirements

%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,10pt, screen]{acmart}
\settopmatter{}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
%\AtBeginDocument{%
%  \providecommand\BibTeX{{%
%    Bib\TeX}}}
\startPage{1}
\bibliographystyle{ACM-Reference-Format}

@@

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{rightsretained}
\acmDOI{XXXXXXX.XXXXXXX}
\acmYear{2024}
\copyrightyear{2024}
\acmSubmissionID{}
\acmISBN{}
%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[CPP '24]{Proceedings of the 13th ACM SIGPLAN International Conference on Certified Programs and Proofs}{Jan 15--16, 2024}{London, United Kingdom}
\acmBooktitle{Proceedings of the 13th ACM SIGPLAN International Conference on Certified Programs and Proofs (CPP '24), Jan 15--16, 2024, London, United Kingdom}

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{Duc-Than Nguyen}
\email{dnguye96@uic.edu}
\orcid{https://orcid.org/0000-0002-6810-897X}
\affiliation{\institution{University of Illinois at Chicago}\streetaddress{}\city{Chicago}\state{IL}\country{USA}\postcode{}}

\author{Lennart Beringer}
\email{eberinge@cs.princeton.edu}
\orcid{https://orcid.org/0000-0002-1570-3492}
\affiliation{\institution{Princeton University}\streetaddress{}\city{Princeton}\state{NJ}\country{USA}\postcode{}}

\author{William Mansky}
\email{mansky1@uic.edu}
\orcid{https://orcid.org/0000-0002-5351-895X}
\affiliation{\institution{University of Illinois at Chicago}\streetaddress{}\city{Chicago}\state{IL}\country{USA}\postcode{}}

\author{Shengyi Wang}
\email{shengyiw@princeton.edu}
\orcid{https://orcid.org/0000-0002-2286-8703}
\affiliation{\institution{Princeton University}\streetaddress{}\city{Princeton}\state{NJ}\country{USA}\postcode{}}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
%\renewcommand{\shortauthors}{Trovato et al.}

>>>>

%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,screen]{acmart}
\settopmatter{}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
%\AtBeginDocument{%
%  \providecommand\BibTeX{{%
%    Bib\TeX}}}
\startPage{1}
\bibliographystyle{ACM-Reference-Format}

@@

%%% The following is specific to CPP '24 and the paper
%%% 'Compositional Verification of Concurrent C Programs with Search Structure Templates'
%%% by Duc-Than Nguyen, Lennart Beringer, William Mansky, and Shengyi Wang.
%%%
\setcopyright{acmlicensed}
\acmDOI{10.1145/3636501.3636940}
\acmYear{2024}
\copyrightyear{2024}
\acmSubmissionID{poplws24cppmain-p2-p}
\acmISBN{979-8-4007-0488-8/24/01}
\acmConference[CPP '24]{Proceedings of the 13th ACM SIGPLAN International Conference on Certified Programs and Proofs}{January 15--16, 2024}{London, UK}
\acmBooktitle{Proceedings of the 13th ACM SIGPLAN International Conference on Certified Programs and Proofs (CPP '24), January 15--16, 2024, London, UK}
\received{2023-09-19}
\received[accepted]{2023-11-25}

@@

\author{Duc-Than Nguyen}
\orcid{0000-0002-6810-897X}
\affiliation{%
	\institution{University of Illinois at Chicago}
	\city{}
	\country{USA}
}
\email{dnguye96@uic.edu}

\author{Lennart Beringer}
\orcid{0000-0002-1570-3492}
\affiliation{%
	\institution{Princeton University}
	\city{}
	\country{USA}
}
\email{eberinge@cs.princeton.edu}

\author{William Mansky}
\orcid{0000-0002-5351-895X}
\affiliation{%
	\institution{University of Illinois at Chicago}
	\city{}
	\country{USA}
}
\email{mansky1@uic.edu}

\author{Shengyi Wang}
\orcid{0000-0002-2286-8703}
\affiliation{%
	\institution{Princeton University}
	\city{}
	\country{USA}
}
\email{shengyiw@princeton.edu}
%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
%\renewcommand{\shortauthors}{Trovato et al.}
